Linear analysis of the vertical shear instability in astrophysical disks

### 2015-02-11 numerical.tex
minor updates

Fig. \ref{gcorr_compare_vnoniso} plots the fundamental VSI growth
rates as a function of $\beta$ for $\gamma\in[1.4,2.5]$. For
comparison with \cite{nelson13} we consider 
$\beta\in[10^{-2},10^2]$. In agreement with \citeauthor{nelson13}, in
the neutrally-stratified case $\gamma=\Gamma$ the disk is unstable
even for $\beta\gg 1$. (Note that in the adiabatic limit
$\beta\to\infty$ this disk can be unstable according to the
Solberg-Hoiland criterion, Eq. \ref{solberg2}.)

>>>>

Fig. \ref{gcorr_compare_vnoniso} plots the fundamental VSI growth
rates as a function of $\beta$ for $\gamma\in[1.4,2.5]$. In agreement with \citeauthor{nelson13}, in 
the neutrally-stratified case $\gamma=\Gamma$ the disk is unstable 
even for $\beta\gg 1$. (Note that in the adiabatic limit 
this disk can be unstable according to the
Solberg-Hoiland criterion, Eq. \ref{solberg2}.)
